### 2019-07-23 thesis.tex
*** empty log message ***

Space plasmas are observed in a vast range of temperature, density, magnetic
field strengths and scale lengths. However, in most of the cases, models used
to describe processes

>>>>

The theory developed during this graduate research has relevant contributions in
the study of the combined action of nonlinear kinetic plasma instabilities and
collisional processes in plasmas. This new approach might help us to elucidate
the fundamental physics behind critical features observed in the solar plasma.
Besides solar physics, the present formalism, due to its underlying character,
can be extended to the plasma of different astrophysical environments and even
laboratory plasmas. In this appendix, we will make a brief revision on solar
physics, pointing out the phenomena that are associated with our model.
